Probability Distribution Checks

### 2017-06-15 Analysis.Rmd
Update probability distribution checks and analysis for tiller sheath blight incidence

#### Iterations
Fitting the models with the default iterations resulted in some less than
acceptable models. Because of this, the number of iterations has been increased,
`nitt = 5e+05` and `burnin = 5000` and `thin = 100`. This results in much
smaller errors for random effects and better models.

## Setup
Use `set.seed()` for reproducibility.

@@

### 2015 Tiller Sheath Blight Incidence Model
```{r 2015_TShB_incidence}

# Separate the TRT column into the two treatments for analysis
AUDPS <- separate(data = AUDPS, col = TRT, sep = "_", into = c("WMGT", "NRTE"))

eprior <- list(R = list(V = 1, nu = 0.02),
               G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
TShB_incidence_lmm_2015 <- MCMCglmm(AUDPS ~ WMGT * NRTE,
                                    random = ~REP, 
                          data = as.data.frame(AUDPS[AUDPS$YEAR == 2015, ]),
                          verbose = FALSE,
                          prior = eprior,
                          nitt = 5e+05,
                          burnin = 5000,
                          thin = 100,
                          pr = TRUE)

@@

### 2016 Tiller Sheath Blight Incidence Model
```{r 2016_TShB_incidence}

eprior <- list(R = list(V = 1, nu = 0.02),
               G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
TShB_incidence_lmm_2016 <- MCMCglmm(AUDPS ~ WMGT * NRTE, 
                                    random = ~REP, 
                          data = as.data.frame(AUDPS[AUDPS$YEAR == 2016, ]),
                          verbose = FALSE,
                          prior = eprior,
                          nitt = 5e+05,
                          burnin = 5000,
                          thin = 100,
                          pr = TRUE)

@@

# Conclusions

@@

None of the treatments in either year, 2015 or 2016, were significant. The
see `pMCMC` values and also posterior graphs. There is a large amount of overlap
in all of the posterior graphs.

@@

# R Session Info
```{r session_info}
devtools::session_info()
```

>>>>

#### Iterations

Fitting the models with the default iterations resulted in some less than
acceptable models. Because of this, the number of iterations has been increased,
`nitt = 5e+05` and `burnin = 5000` and `thin = 100`. This results in much
smaller errors for random effects and better models.

## Setup

Use `set.seed()` for reproducibility.

@@

### 2015 Tiller Sheath Blight Incidence Model

```{r 2015_TShB_incidence}

# Separate the TRT column into the two treatments for analysis
AUDPS <- separate(data = AUDPS, col = TRT, sep = "_", into = c("WMGT", "NRTE"))
AUDPS <- mutate_at(AUDPS, .funs = factor, .cols = c("NRTE", "WMGT"))

eprior <- list(R = list(V = 1, nu = 0.02),
               G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
TShB_incidence_lmm_2015 <- MCMCglmm(TShB_inc_AUDPS ~ WMGT * NRTE,
                                    random = ~REP, 
                          data = as.data.frame(AUDPS[AUDPS$YEAR == 2015, ]),
                          verbose = FALSE,
                          prior = eprior,
                          nitt = 5e+05,
                          burnin = 5000,
                          thin = 100,
                          pr = TRUE)

@@

### 2016 Tiller Sheath Blight Incidence Model

```{r 2016_TShB_incidence}

eprior <- list(R = list(V = 1, nu = 0.02),
               G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
TShB_incidence_lmm_2016 <- MCMCglmm(TShB_inc_AUDPS ~ WMGT * NRTE, 
                                    random = ~REP, 
                          data = as.data.frame(AUDPS[AUDPS$YEAR == 2016, ]),
                          verbose = FALSE,
                          prior = eprior,
                          nitt = 5e+05,
                          burnin = 5000,
                          thin = 100,
                          pr = TRUE)

@@

## Conclusions

### Tiller Sheath Blight Incidence

In 2015 the highest N treatment was significant, in 2016 both the flooded water management and the N rates were significant.

@@

@@

## R Session Info

```{r session_info, echo=FALSE}
devtools::session_info()
```

### 2017-06-15 Probability_distribution_checks.Rmd
Update probability distribution checks and analysis for tiller sheath blight incidence

Here we check the probability distribution that best fits these data. I'm following a method from http://ase.tufts.edu/gsc/gradresources/guidetomixedmodelsinr/mixed%20model%20guide.html. As you see in that guide, there are several distributions that can be checked, however, the data both fit a normal distribution.

## 2015 Check probability distribution fit for tiller sheath blight incidence

```{r, results='hide', message=FALSE, warning=FALSE}
AUDPS15 <- subset(AUDPS, YEAR == "2015")
f1 <- fitdist(AUDPS15$AUDPS, "norm")
plot(f1)
car::qqp(AUDPS15$AUDPS, "norm")

@@

## 2016 Check probability distribution fit for tiller sheath blight incidence

```{r, results='hide', message=FALSE, warning=FALSE}
AUDPS156 <- subset(AUDPS, YEAR == "2016")
f1 <- fitdist(AUDPS156$AUDPS, "norm")
plot(f1)
car::qqp(AUDPS156$AUDPS, "norm")

@@

To read the graphs, we want to select a distribution where most of the points fall between the dotted red lines. On the y-axis are the observations and on the x-axis the quantiles modelled by the distribution. A perfect distribution fit is represented by the solid red line and the dashed red lines are the confidence intervals of the perfect distribution fit. Here both sets of data fit a normal distribution.

>>>>

Here we check the probability distribution that best fits these data. I'm following a method from http://ase.tufts.edu/gsc/gradresources/guidetomixedmodelsinr/mixed%20model%20guide.html. As you see in that guide, there are several distributions that can be checked. However, in these data only normal and exponential

## 2015

### Check probability distribution fit for tiller sheath blight incidence

#### Normal

```{r 2015_inc_norm, results='hide', message=FALSE, warning=FALSE}
AUDPS15 <- subset(AUDPS, YEAR == "2015")
f1 <- fitdist(AUDPS15$TShB_inc_AUDPS, "norm")
plot(f1)

car::qqp(AUDPS15$TShB_inc_AUDPS, "norm")
```

#### Exponential

```{r 2015_inc_exp, results='hide', message=FALSE, warning=FALSE}

f1 <- fitdist(AUDPS15$TShB_inc_AUDPS, "exp")
plot(f1)
car::qqp(AUDPS15$TShB_inc_AUDPS, "exp")
car::qqp(AUDPS15$TShB_inc_AUDPS, "lnorm")

@@

## 2016

### Check probability distribution fit for tiller sheath blight incidence

#### Normal

```{r, 2016_inc_norm, results='hide', message=FALSE, warning=FALSE}
AUDPS16 <- subset(AUDPS, YEAR == "2016")
 f1 <- fitdist(AUDPS16$TShB_inc_AUDPS, "norm")
plot(f1)

car::qqp(AUDPS16$TShB_inc_AUDPS, "norm")
```

#### Exponential

```{r 2016_inc_exp, results='hide', message=FALSE, warning=FALSE}

f1 <- fitdist(AUDPS16$TShB_inc_AUDPS, "exp")
plot(f1)

car::qqp(AUDPS16$TShB_inc_AUDPS, "exp")
```

@@

To read the graphs, we want to select a distribution where most of the points fall between the dotted red lines. On the y-axis are the observations and on the x-axis the quantiles modelled by the distribution. A perfect distribution fit is represented by the solid red line and the dashed red lines are the confidence intervals of the perfect distribution fit.

### Tiller Incidence Distributions

The 2015 data fit an exponential distribution while the 2016 data fit a normal distribution.
